# Alltag und Sex - Descriptives {.tabset .tabset-sticky}

```{r}
source("0_helpers.R")
load("data/cleaned.rdata")
opts_chunk$set(warning = F, message = F, error = T)

library(knitr)
opts_chunk$set(fig.width = 9, fig.height = 7, cache = T, warning = F, message = F, cache = F, error = T)
```

## Who completed what? {.tabset .tabset-sticky}

### Participant funnel

```{r}
began_s1_demo = sum(!is.na(s1_demo$created))
ended_s1_demo = sum(!is.na(s1_demo$ended))
diary <- s1_filter %>% left_join(diary, by = c('session', 'short'), suffix = c("_filter", ""))
ended_pre = diary %>% filter(!is.na(ended_initial)) %>% ungroup() %>% summarise(n = n_distinct(session)) %>% pull(n)
diary %>% group_by(gets_paid) %>% summarise(n = sum(!is.na(ended_initial[!duplicated(session)]), n = n_distinct(session)))
at_least_one_diary_entry = diary %>% group_by(session) %>% summarise(n = n_nonmissing(ended_diary)) %>% filter(n >= 1) %>% nrow()
at_least_20_diary_entries = diary %>% group_by(session) %>% summarise(n = n_nonmissing(ended_diary)) %>% filter(n >= 20) %>% nrow()
at_least_50_diary_entries = diary %>% group_by(session) %>% summarise(n = n_nonmissing(ended_diary)) %>% filter(n >= 50) %>% nrow()

in_relationship = sum(s1_demo$hetero_relationship, na.rm = T)
singles = sum(! s1_demo$hetero_relationship, na.rm = T)

at_least_one_diary_entry = s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 1) %>% nrow()
at_least_20_diary_entries = s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 20) %>% nrow()
at_least_50_diary_entries = s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 50) %>% nrow()

mean_diary_entries <- s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% summarise(mean(n))

mean_diary_entries_by_payment <- s1_filter %>% 
  select(-ended) %>% left_join(s3_daily, by = 'session') %>% 
  group_by(gets_paid, session) %>%
  summarise(n = n_nonmissing(ended)) %>% 
  filter(n > 0) %>% 
  group_by(gets_paid) %>% 
  summarise(responses = mean(n), n = n_distinct(session))

response_rate_over_time <- diary %>% filter(day_number > 0, day_number < 70) %>% 
    left_join(s1_filter, by = 'session', suffix = c("", "_filter")) %>% 
  left_join(mean_diary_entries_by_payment) %>% 
  group_by(gets_paid, day_number) %>% 
  summarise(entries = n_nonmissing(ended_diary),
            rr = entries / unique(n))
ggplot(response_rate_over_time, aes(day_number, rr, colour = gets_paid)) + geom_point() +
    ggtitle("Response rate over time", "for people who started the diary") + ylim(0,1)

mean_diary_entries_finishers <- s4_followup %>% select(-ended) %>% left_join(s3_daily, by = 'session') %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% summarise(mean(n))

response_rate_over_time <- s4_followup %>% select(-ended) %>% 
  left_join(diary %>% select(session, day_number, created_diary, ended_diary)) %>% filter(day_number > 0, day_number < 70) %>% 
  left_join(s1_filter, by = 'session', suffix = c("", "_filter")) %>% 
  left_join(mean_diary_entries_by_payment) %>% 
  group_by(gets_paid, day_number) %>% 
  summarise(entries = n_nonmissing(ended_diary),
            rr = entries / unique(n))
ggplot(response_rate_over_time, aes(day_number, rr, colour = gets_paid)) + 
  geom_point() +
    ggtitle("Response rate over time", "for people who finished the diary") + ylim(0,1)

nsmt2d_over_time <- s4_followup %>% select(-ended) %>% 
  left_join(diary %>% select(session, day_number, never_skipped_more_than_2, created_diary, ended_diary)) %>% 
  left_join(s1_filter, by = 'session', suffix = c("", "_filter")) %>% 
  left_join(mean_diary_entries_by_payment) %>% 
  group_by(gets_paid, day_number) %>% 
  summarise(entries = sum(as.numeric(never_skipped_more_than_2), na.rm = T),
            rr = entries / unique(n))

ggplot(nsmt2d_over_time, aes(day_number, rr, colour = gets_paid)) + 
  geom_point() +
    ggtitle("Percentage who never skipped more than two days over time", "for people who finished the diary") + ylim(0,1)


mean_finishing_personality_by_payment <- s1_demo %>% 
  left_join(s1_filter, by = 'session', suffix = c("_demo", "")) %>% 
  left_join(s2_initial,by ='session', suffix = c("", "_initial")) %>% 
  group_by(gets_paid) %>% 
  summarise(finish_demo = n_nonmissing(ended_demo), 
            finish_initial = n_nonmissing(ended_initial), n = n(),
            prc_ini_over_demo = round(100*finish_initial/finish_demo),
            consc = mean(bfi_consc,na.rm=T))
kable(mean_finishing_personality_by_payment)

mean_finishing_follow_up_by_payment <- s1_filter %>% select(-ended) %>% right_join(s2_initial,by ='session') %>% left_join(s4_followup, by = 'session', suffix = c("_initial", "_followup")) %>% group_by(gets_paid) %>% summarise(followup = n_nonmissing(ended_followup), initial = n_nonmissing(ended_initial), n(), prc_fu_over_initial = round(100*followup/initial))
kable(mean_finishing_follow_up_by_payment)

fertile_known_man_known = diary_social %>% group_by(session, created) %>% 
  summarise(n = n_nonmissing(person_attractiveness_short_term)) %>% 
  group_by(session) %>% summarise(n = sum(n)) # fertility known, man known
fertile_known_man_known$n %>% qplot() + xlim(1,NA)

fertile_known_person_known = diary_social %>% group_by(session, created) %>% 
  summarise(n = n_nonmissing(person_sex)) %>% 
  group_by(session) %>% summarise(n = sum(n)) # fertility known, man known

finished_timespent = s4_timespent %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 1) %>% nrow()
timespent_gt3 = s4_timespent %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n > 3) %>% nrow()
timespent_men = network %>% group_by(session) %>% filter(person_sex == 2, person_relationship_to_anchor != "biological_relative") %>% summarise(n = n_nonmissing(ended)) %>% filter(n > 0) %>% nrow()
timespent_3men = network %>% group_by(session) %>% filter(person_sex == 2, person_relationship_to_anchor != "biological_relative") %>% summarise(n = n_nonmissing(ended)) %>% filter(n > 2) %>% nrow()

fertile_known_man_known_participants = fertile_known_man_known %>% filter(n > 0) %>% nrow()
fertile_known_person_known_participants = fertile_known_person_known %>% filter(n > 0) %>% nrow()

finished_followup = sum(!is.na(s4_followup$ended))

# all_surveys %>% mutate(
#   should_be_done = created_demo + days(70) < today()
# ) %>% filter(should_be_done == T) %>% xtabs(~ is.na(ended), .)

# all_surveys %>% mutate(
# should_be_done = created_demo + days(70) < today()
# ) %>% left_join(s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended))) %>% 
#  filter(should_be_done == T, n > 40) %>% xtabs(~ is.na(ended), .)

all_surveys %>% mutate(should_be_done = created_demo + days(70) < today()) %>%
 left_join( s4_timespent %>% group_by(session) %>% summarise(n_timespent = n_nonmissing(ended)), by = 'session') %>% 
 filter(hetero_relationship == 0, should_be_done == T, n_timespent > 0, !is.na(n_timespent)) %>% nrow()

all_surveys %>% mutate(should_be_done = created_demo + days(70) < today()) %>%
 left_join( s4_timespent %>% group_by(session) %>% summarise(n_timespent =  n_nonmissing(ended)), by = 'session') %>% 
 filter(hetero_relationship == 0 & should_be_done == T & (is.na(n_timespent) | n_timespent == 0)) %>% nrow()
```

1. __`r began_s1_demo`__ signed up for the study.
2. __`r ended_s1_demo`__ finished the demographics (`r singles` singles, `r in_relationship` in relationship).
2. __`r ended_pre`__ finished the demographic and personality questionnaires.
3. __`r at_least_one_diary_entry`__ submitted at least one diary entry (>= 20: `r at_least_20_diary_entries`, >= 50 `r at_least_50_diary_entries`). On average participants completed `r mean_diary_entries` diary entries.
4. `r finished_timespent` singles reported information on least one person mentioned during the diary (>3: `r timespent_gt3`, at least one man who wasn't biologically related: `r timespent_men`, >2men: `r timespent_3men`). 
5. __`r finished_followup`__ (`r round(100*finished_followup/ended_pre)`% of those who finished the intake survey) finished the follow-up survey. Finishers completed on average `r mean_diary_entries_finishers` diary entries.


## Exclusion {.tabset .tabset-sticky}

```{r}
all_surveys$included <- TRUE
diary$included_d = TRUE

pipeline = list()
excluded_old = NULL
all_surveys = all_surveys %>% mutate(included = if_else(included, 
                    !is.na(ended_demo) , F))
newly_excluded = sum( !all_surveys$included)

diary$included_d <- TRUE

pipeline_days = list()
excluded_old_days = NULL

diary_social$included_s <- TRUE

pipeline_social= list()
excluded_old_social = NULL


pipeline$not_finished_demo = n_excluded(all_surveys$included)

sum(all_surveys$included)
```

```{r}
sum(diary$included_d)

diary = diary %>% mutate(included_d = if_else(included_d, 
                    !is.na(ended_demo) , F))
newly_excluded_days = sum( !diary$included_d)


pipeline$demo_days = n_excluded_days(diary$included_d)
sum(diary$included_d)

```

```{r}
sum(diary_social$included_s)

diary_social = diary_social %>% mutate(included_s = if_else(included_s, 
                     !is.na(ended_demo) , F))
newly_excluded_social = sum( !diary_social$included_s)

pipeline_social$days_social_not_single = n_excluded_social(diary_social$included_s)

sum(diary_social$included_s)

```

#### ended initial 

```{r}
all_surveys = all_surveys %>% mutate(included = if_else(included, 
                    !is.na(ended_initial) , F))
newly_excluded = sum( !all_surveys$included)


pipeline$initial = n_excluded(all_surveys$included)

sum(all_surveys$included)
``` 

```{r}

diary = diary %>% mutate(included_d = if_else(included_d, 
                    !is.na(ended_initial) , F))
newly_excluded_days = sum( !diary$included_d)


pipeline$initial_days = n_excluded_days(diary$included_d)
sum(diary$included_d)

``` 

```{r}
diary_social = diary_social %>% mutate(included_s = if_else(included_s, 
                     !is.na(ended_initial), F))
newly_excluded_social = sum( !diary_social$included_s)

      
pipeline_social$initial_social = n_excluded_social(diary_social$included_s)

sum(diary_social$included_s)
```

### regular cycle 
regular = 1 
irregular = 0
```{r}
crosstabs(~ menstruation_regular + hormonal_contraception, data = all_surveys)
irregular = count(all_surveys %>% filter(menstruation_regular == 0 & !is.na(ended_initial)  ))


irregular_missing = count(all_surveys %>% filter(menstruation_regular == 0 | is.na(menstruation_regular & !is.na(ended_initial))))

```

3. __`r irregular`__ women with irregular cycle.
4. __`r irregular_missing`__ women with irregular cycle and missings.

```{r}

all_surveys = all_surveys %>% mutate(included = if_else(included,
                                                        if_else(menstruation_regular != 0, T,F,F),F))
newly_excluded = sum( !all_surveys$included)

pipeline$irregular_cycle = n_excluded(all_surveys$included)

sum(all_surveys$included)

# xtabs(~ hetero_relationship + included, data = all_surveys)
```

#### exlcuded days 

```{r}
diary <- diary %>% ungroup()
d_irregular = count(diary %>% filter(menstruation_regular == 0 & !is.na(ended_initial) ))


d_irregular_missing = count(diary %>% filter(menstruation_regular == 0 | is.na(menstruation_regular & !is.na(ended_initial))))

```
3.1 __`r d_irregular`__ days of women with irregular cycle.
4.1 __`r d_irregular_missing`__ days of women with irregular cycle and missings.

```{r}
diary = diary %>% mutate(included_d = if_else(included_d, 
                    if_else( menstruation_regular != 0, T, F, F), F))
newly_excluded_days = sum( !diary$included_d)

      
pipeline_days$days_with_irregular_cycle = n_excluded_days(diary$included_d)
sum(diary$included_d)
```

#### exlcusion social diary 

```{r}
s_irregular = count(diary_social %>% filter(menstruation_regular == 0  & !is.na(ended)))


s_irregular_missing = count(diary_social %>% filter(menstruation_regular == 0 | is.na(menstruation_regular & !is.na(ended_initial))))

```
3.2 __`r s_irregular`__ days of women with irregular cycle.
4.2 __`r s_irregular_missing`__ days of women with irregular cycle and missings.

```{r}
diary_social = diary_social %>% mutate(included_s = if_else(included_s, 
                    if_else( menstruation_regular != 0, T, F, F), F))
newly_excluded_social = sum( !diary_social$included_s)

pipeline_social$days_social_irregular_cycle = n_excluded_social(diary_social$included_s)

sum(diary_social$included_s)
```

### cycle length 
```{r}
# all_surveys %>% filter(hetero_relationship == 0 & !is.na(ended_initial) & is.na(menstruation_length)) %>% View()

too_short_cycle = count(all_surveys %>% filter(menstruation_length_groups == 'short' & !is.na(ended_initial)))

too_short_and_missing = count(all_surveys %>%  filter(menstruation_length_groups == 'short' | is.na(menstruation_length_groups) & !is.na(ended_initial)))

```
1. __`r too_short_cycle`__ women with too short cycle.
2. __`r too_short_and_missing`__ women with too short cycle and missings. 



```{r}
all_surveys = all_surveys %>% mutate(included = if_else(included, 
                    menstruation_length > 19, F))
newly_excluded = sum( !all_surveys$included)

      
pipeline$too_short_cycles = n_excluded(all_surveys$included)
sum(all_surveys$included)
```

#### days excluded
```{r}
d_too_short = count(diary %>% filter(menstruation_length > 19 & !is.na(ended_initial)))
d_too_short_missing = count(diary %>% filter(menstruation_length > 19 & !is.na(ended_initial) | is.na(menstruation_length)))

```

1.1 __`r d_too_short`__ days of women with too short cycle.
2.1 __`r d_too_short_missing`__ days of women with too short cycle and missing.


```{r}
diary = diary %>% mutate(included_d = if_else(included_d, 
                    menstruation_length > 19, F))
newly_excluded_days = sum( !diary$included_d)

      
pipeline_days$days_with_too_short_cycles = n_excluded_days(diary$included_d)

sum(diary$included_d)
```

#### exclusion social diary
```{r}
ds_too_short = count(diary_social %>% filter(menstruation_length > 19 & !is.na(ended_initial) ))
ds_too_short_m = count(diary_social %>%
                         filter(menstruation_length > 19 | 
                                  is.na(menstruation_length) & 
                                          !is.na(ended_initial)))
```

1.2 __`r ds_too_short`__ days of women with too short cycle.
2.2 __`r ds_too_short_m`__ days of women with too short cycle and missings.


```{r}
diary_social = diary_social %>% mutate(included_s = if_else(included_s, 
                    menstruation_length > 19, F))
newly_excluded_social = sum( !diary_social$included_s)

      
pipeline_social$days_social_short_cycles = n_excluded_social(diary_social$included_s)

sum(diary_social$included_s)
```


### age 

```{r}
older_than_50 = count(all_surveys %>% filter(age >= 50  & !is.na(ended_initial)))

too_old_missing = count(all_surveys %>% filter(age >= 50 | is.na(age) & !is.na(ended_initial)))

```

5. __`r older_than_50`__ women older than 50.
6. __`r too_old_missing`__ women older than 50 and missings.


```{r}
all_surveys = all_surveys %>% mutate(included = if_else(included, 
                                                          age < 50, F))

newly_excluded = sum( !all_surveys$included)


pipeline$older_than_50 = n_excluded(all_surveys$included)

sum(all_surveys$included)
```

#### excluded days 

```{r}
d_older_than_50 = count(diary %>% filter(age >= 50 & !is.na(ended_initial)))

d_too_old_missing = count(diary %>% filter(age >= 50 | is.na(age) & !is.na(ended_initial)))
```

5.1 __`r d_older_than_50`__ days of women older than 50.
6.1 __`r d_too_old_missing`__ days of women older than 50 and missings.

```{r}
diary = diary %>% mutate(included_d = if_else(included_d, 
                    age < 50, F))
newly_excluded_days = sum( !diary$included_d)

      
pipeline_days$days_age = n_excluded_days(diary$included_d)

sum(diary$included_d)
```

#### exclusion social diary

```{r}
s_older_than_50 = count(diary_social %>% filter(age >= 50 & !is.na(ended_initial)))

s_too_old_missing = count(diary_social %>% filter(age >= 50 | is.na(age) & !is.na(ended_initial)))

```

5.2 __`s d_older_than_50`__ days of women older than 50.
6.2 __`s d_too_old_missing`__ days of women older than 50 and missings.

```{r}
diary_social = diary_social %>% mutate(included_s = if_else(included_s, 
                   age < 50, F))
newly_excluded_social = sum( !diary_social$included_s)

pipeline_social$days_social_age = n_excluded_social(diary_social$included_s)

sum(diary_social$included_s)

```

### menopausal 
only asked women older than 43
1 = menopausal 
2 = menopause

```{r}
menopause = count(all_surveys %>% filter(menopause_yes == 1 | menopause_yes == 2 & !is.na(ended_initial)))

non_menopausal = count(all_surveys %>% filter(menopause_yes == 3 | is.na(menopause_yes) & !is.na(ended_initial)))
```

7. __`r menopause`__ menopausal women and women in their menopause.
8. __`r non_menopausal`__ non-menopausal women and women younger than 43. 

```{r}
all_surveys = all_surveys %>% mutate(included = if_else(included, 
                                                        menopause_yes ==3 |
                                                      is.na(menopause_yes), F))
newly_excluded = sum( !all_surveys$included)

pipeline$menopausal = n_excluded(all_surveys$included)

sum(all_surveys$included)
```

#### excluded days 

```{r}
d_menopause = count(diary %>% filter(menopause_yes == 1 | menopause_yes == 2 & !is.na(ended_initial) ))

d_non_menopausal = count(diary %>% filter(menopause_yes == 3 | is.na(menopause_yes) & !is.na(ended_initial)))
```

7.1 __`r d_menopause`__ days of menopausal women and women in their menopause.
8.1 __`r d_non_menopausal`__ days of non-menopausal women and women younger than 43. 

```{r}
diary = diary %>% mutate(included_d = if_else(included_d, 
                    menopause_yes == 3 |
                      is.na(menopause_yes), F))
newly_excluded_days = sum( !diary$included_d)

      
pipeline_days$days_menopause = n_excluded_days(diary$included_d)
sum(diary$included_d)
```

#### exclusion social diary 
```{r}
s_menopause = count(diary_social %>% filter(menopause_yes == 1 | menopause_yes == 2 & !is.na(ended_initial) ))

s_non_menopausal = count(diary_social %>% filter(menopause_yes == 3 | is.na(menopause_yes) & !is.na(ended_initial)))
```

7.2 __`r s_menopause`__ days of menopausal women and women in their menopause.
8.2 __`r s_non_menopausal`__ days of non-menopausal women and women younger than 43. 

```{r}
diary_social = diary_social %>% mutate(included_s = if_else(included_s, 
                     menopause_yes == 3 |
                      is.na(menopause_yes), F))
newly_excluded_social = sum( !diary_social$included_s)

pipeline_social$days_social_menopause = n_excluded_social(diary_social$included_s)

sum(diary_social$included_s)
```

### pregnant

```{r}
pregnant = count(all_surveys %>% filter(pregnant == 1  & !is.na(ended_initial)))
pregnant_missing = count(all_surveys %>% filter(pregnant == 1 | is.na(pregnant) & !is.na(ended_initial)))
```
9. __`r pregnant`__ pregnant women.
10. __`r pregnant_missing`__ pregnant women and missings. 


```{r}
all_surveys = all_surveys %>% mutate(included = if_else(included, 
                                                        pregnant != 1, F))

newly_excluded = sum( !all_surveys$included)

pipeline$pregnant = n_excluded(all_surveys$included)

sum(all_surveys$included)
```

#### excluded days 

```{r}
d_pregnant = count(diary %>% filter(pregnant == 1 & !is.na(ended_initial) ))
d_pregnant_missing = count(diary %>% filter(pregnant == 1 | is.na(pregnant) & !is.na(ended_initial)))
```

9.1 __`r d_pregnant`__ days of pregnant women.
10.1 __`r d_pregnant_missing`__ days of pregnant women and missings.  

```{r}
diary = diary %>% mutate(included_d = if_else(included_d, 
                    pregnant != 1, F))
newly_excluded_days = sum( !diary$included_d)

pipeline_days$days_pregnant = n_excluded_days(diary$included_d)
sum(diary$included_d)
```

#### exclusion social diary
```{r}
s_pregnant = count(diary_social %>% filter(pregnant == 1 &!is.na(ended_initial) ))
s_pregnant_missing = count(diary_social %>% filter(pregnant == 1 | is.na(pregnant) & !is.na(ended_initial)))
```

9.2 __`r s_pregnant`__ days of pregnant women.
10.2 __`r s_pregnant_missing`__ days of pregnant women and missings. 

```{r}
diary_social = diary_social %>% mutate(included_s = if_else(included_s, 
                     pregnant != 1, F))
newly_excluded_social = sum( !diary_social$included_s)

pipeline_social$days_social_pregnant = n_excluded_social(diary_social$included_s)
sum(diary_social$included_s)
```

### breast-feeding
```{r}
breast_feeding = count(all_surveys %>% filter(breast_feeding == 1 & !is.na(ended_initial) ))

breast_feeding_missing = count(all_surveys %>% filter(breast_feeding == 1| is.na(breast_feeding) & !is.na(ended_initial)))

```

11. __`r breast_feeding`__ women breast-feeding.
12. __`r breast_feeding_missing`__ women breast-feeding and missings. 

```{r}
all_surveys = all_surveys %>% mutate(included = if_else(included, 
                                                        breast_feeding != 1, F))

newly_excluded = sum( !all_surveys$included)

pipeline$breastfeeding = n_excluded(all_surveys$included)

sum(all_surveys$included)
```

#### excluded days 

```{r}
d_breast_feeding = count(diary %>% filter(breast_feeding == 1 & !is.na(ended_initial) ))

d_breast_feeding_missing = count(diary %>% filter(breast_feeding == 1| is.na(breast_feeding) & !is.na(ended_initial)))
```

11.1 __`r d_breast_feeding`__ days of breast-feeding women.
12.1 __`r d_breast_feeding_missing`__ days of breast-feeding women and missings. 

```{r}
diary = diary %>% mutate(included_d = if_else(included_d, 
                    breast_feeding != 1, F))
newly_excluded_days = sum( !diary$included_d)

pipeline_days$days_breast_feeding = n_excluded_days(diary$included_d)

sum(diary$included_d)
```

#### exclusion social diary 

```{r}
s_breast_feeding = count(diary_social %>% filter(breast_feeding == 1 & !is.na(ended_initial) ))

s_breast_feeding_missing = count(diary_social %>% filter(breast_feeding == 1| is.na(breast_feeding) & !is.na(ended_initial)))
```

11.2 __`r s_breast_feeding`__ days of breast-feeding women.
12.2 __`r s_breast_feeding_missing`__ days of breast-feeding women and missings.

```{r}
diary_social = diary_social %>% mutate(included_s = if_else(included_s, 
                     breast_feeding != 1, F))
newly_excluded_social = sum( !diary_social$included_s)

pipeline_social$days_social_breast_feeding = n_excluded_social(diary_social$included_s)
sum(diary_social$included_s)
```


### homosexual

```{r}
homosexual = count(all_surveys %>% filter(sex_orientation >= 4 & !is.na(ended_initial) ))

homosexual_missing = count(all_surveys %>% filter(sex_orientation >= 4 |is.na(sex_orientation) & !is.na(ended_initial)))

```

13. __`r homosexual`__ heterosexual women.
14. __`r homosexual_missing`__ heterosexual women and missings. 


```{r}
all_surveys = all_surveys %>% mutate(included = if_else(included, 
                    sex_orientation < 4, F))
newly_excluded = sum( !all_surveys$included)


pipeline$heterosexual = n_excluded(all_surveys$included)
sum(all_surveys$included)
```

#### excluded days 

```{r}
d_heterosexual = count(diary %>% filter(sex_orientation >= 4 & !is.na(ended_initial) ))

d_heterosexual_missing = count(diary %>% filter(sex_orientation >= 4 |is.na(sex_orientation) & !is.na(ended_initial)))
``` 

13.1 __`r d_heterosexual`__ days of heterosexual women.
14.1 __`r d_heterosexual_missing`__ days of heterosexual women and missings. 

```{r}
diary = diary %>% mutate(included_d = if_else(included_d, 
                    sex_orientation < 4, F))
newly_excluded_days = sum( !diary$included_d)

pipeline_days$days_heterosexual = n_excluded_days(diary$included_d)
sum(diary$included_d)
```

#### exclusion social diary
```{r}
s_heterosexual = count(diary_social %>% filter(sex_orientation >= 4 & !is.na(ended_initial) ))

s_heterosexual_missing = count(diary_social %>% filter(sex_orientation >= 4 |is.na(sex_orientation) & !is.na(ended_initial)))
``` 

13.2 __`r s_heterosexual`__ days of heterosexual women.
14.2 __`r s_heterosexual_missing`__ days of heterosexual women and missings.

```{r}
diary_social = diary_social %>% mutate(included_s = if_else(included_s, 
                     sex_orientation < 4, F))
newly_excluded_social = sum( !diary_social$included_s)

pipeline_social$days_social_heterosexual = n_excluded_social(diary_social$included_s)
sum(diary_social$included_s)
```

### change contraception

```{r}

# all_surveys %>% filter(!is.na(ended_initial) ) %>% crosstabs(~ change_to_nonhormonal + change_to_hormonal_contraception, data = .)
```

```{r}
#crosstabs(~ change_contraception, data = all_surveys)
#crosstabs(~ change_to_nonhormonal, data = all_surveys)
#crosstabs(~ change_to_hormonal_contraception, data = all_surveys)
#crosstabs(~ no_relevant_change + change_to_hormonal_contraception, data = all_surveys)

all_surveys = all_surveys %>% mutate(included = if_else(
  condition = included,
  true = if_else(condition = change_to_nonhormonal == 0 & change_to_hormonal_contraception == 0, T, F, T),
  false = F))

newly_excluded = sum( !all_surveys$included, na.rm = T)

pipeline$changed_contraception = n_excluded(all_surveys$included)
sum(all_surveys$included)
```

#### excluded days 
```{r}
# diary %>% filter(!is.na(ended_initial) ) %>% crosstabs(~ change_to_nonhormonal + change_to_hormonal_contraception, data = .)
```

```{r}
diary = diary %>% mutate(included_d = if_else(
  condition = included_d,
  true = if_else(condition = change_to_nonhormonal == 0 & change_to_hormonal_contraception == 0, T, F, T),
  false = F))

newly_excluded_days = sum( !diary$included_d)

pipeline$days_changed_contraception = n_excluded_days(diary$included_d)
sum(diary$included_d)
```

#### exclusion social diary
```{r}
# diary_social %>% filter(!is.na(ended_initial) ) %>% crosstabs(~ change_to_nonhormonal + change_to_hormonal_contraception, data = .)
```

```{r}
diary_social = diary_social %>% mutate(included_s = if_else(
  condition = included_s,
  true = if_else(condition = change_to_nonhormonal == 0 & change_to_hormonal_contraception == 0, T, F, T),
  false = F))

newly_excluded_social = sum( !diary_social$included_s)

pipeline_social$days_social_contraception = n_excluded_social(diary_social$included_s)
sum(diary_social$included_s)
```

### dishonest

```{r}
# crosstabs(~ dishonest_discard, data = diary)
d_dishonest = count(diary %>% filter(dishonest_discard == 1 & !is.na(ended_initial)  ))
```

17. __`r d_dishonest`__ dishonest days.

```{r}
diary = diary %>% mutate(included_d = if_else(included_d, 
                    dishonest_discard != 1, F))
newly_excluded_days = sum( !diary$included_d)

pipeline$dishonest_days = n_excluded_days(diary$included_d)
sum(diary$included_d)
```


#### exclusion social diary 
```{r}
s_dishonest = count(diary_social %>% filter(dishonest_discard == 1 & !is.na(ended_initial)  ))
```

17. __`r s_dishonest`__ dishonest days.

```{r}
diary_social = diary_social %>% mutate(included_s = if_else(included_s, 
                    dishonest_discard != 1, F))
newly_excluded_social = sum( !diary_social$included_s)

pipeline_social$days_social_dishonest = n_excluded_social(diary_social$included_s)
sum(diary_social$included_s)
```



### hormonal contraception last three month for nc 

```{r}
nrow(all_surveys %>% filter(included == T & hormonal_contraception == F & hormonal_contraception_last3m == 1))

nrow(diary %>% filter(included_d == T & hormonal_contraception == F & hormonal_contraception_last3m == 1))

nrow(diary_social %>% filter(included_s == T & hormonal_contraception == F & hormonal_contraception_last3m == 1))

```

```{r}
final_sample= nrow(all_surveys %>% filter(included == T))

single_nc = nrow(all_surveys %>% filter(included == T & hormonal_contraception == F))
single_hc = nrow(all_surveys %>% filter(included == T & hormonal_contraception == T))
```

1. __`r final_sample`__ number of final sample size 
2. __`r single_nc`__ number of singles not taking hormonal contraceptives. 
3. __`r single_hc`__ number of singles taking hormonal contraceptives. 


### no estimated fertility  
```{r}
diary_fertility = nrow(diary %>% filter(included_d == T & !is.na(fertile_fab)))

diary_fertility_hc = nrow(diary %>% filter(included_d == T & !is.na(fertile_fab) & hormonal_contraception == T))
diary_fertility_nc = nrow(diary %>% filter(included_d == T & !is.na(fertile_fab) & hormonal_contraception == F))

social_fertility = nrow(diary_social %>% filter(included_s == T & !is.na(fertile_fab)))
social_fertility_hc = nrow(diary_social %>% filter(included_s == T & !is.na(fertile_fab) & hormonal_contraception == T))
social_fertiliy_nc= nrow(diary_social %>% filter(included_s == T & !is.na(fertile_fab) & hormonal_contraception == F))
```


```{r}
diary = diary %>% mutate(included_d = if_else(included_d, 
                    !is.na(fertile_fab) , F))
newly_excluded_days = sum( !diary$included_d)

pipeline$fertility = n_excluded_days(diary$included_d)
sum(diary$included_d)
```

```{r}
diary_social = diary_social %>% mutate(included_s = if_else(included_s, 
                    !is.na(fertile_fab), F))
newly_excluded_social = sum( !diary_social$included_s)

pipeline_social$fertile = n_excluded_social(diary_social$included_s)
sum(diary_social$included_s)
```



```{r}
final_days= nrow(diary %>% filter(included_d == T))

days_nc= nrow(diary %>% filter(included_d == T & hormonal_contraception == F))
days_hc= nrow(diary %>% filter(included_d == T & hormonal_contraception == T))



social_final = nrow(diary_social %>% filter(included_s ==T))

social_nc= nrow(diary_social %>% filter(included_s == T & hormonal_contraception == F))
social_hc = nrow(diary_social %>% filter(included_s == T & hormonal_contraception == T))


diary_social = diary_social %>% left_join(diary %>% select(session, created_diary, included_d) %>% rename(included_diary = included_d), by = c("session", "created_diary"))
# crosstabs(~ included_diary + included_s, data = diary_social)
diary_social$included_s = diary_social$included_diary
```
4. __`r final_days`__ final number of days we can analyse.
5. __`r days_nc`__ final number of days we can analyse for singles _not_ taking hormonal contraceptives.
6. __`r days_hc`__ final number of days we can analyse for singles taking hormonal contraceptives.
7. __`r social_final`__ final number of days in social diary we can analyse.
8. __`r social_nc`__ final number of days in social diary we can analyse for singles _not_ taking hormonal contraceptives.
9. __`r social_hc`__ final number of days in social diary we can analyse for singles taking hormonal contraceptives.


## Diary days
```{r}
finished_diary_entry = sum(!is.na(s3_daily$ended))
fertility_estimated = sum(!is.na(s3_daily$fertile_fab))
fertility_backwards = sum(!is.na(s3_daily$prc_stirn_b))
fertility_forwards = sum(!is.na(s3_daily$prc_stirn_b_forward_counted))

fertile_known_man_known_days = fertile_known_man_known %>% ungroup() %>% summarise(n = sum(n)) %>% .[["n"]]
fertile_known_person_known_days = fertile_known_person_known %>% ungroup() %>% summarise(n = sum(n)) %>% .[["n"]]
```


1. Number of diary entries total: __`r finished_diary_entry`__.
2. Number of entries where fertility could be estimated: __`r fertility_estimated`__.
    - forward-counted: `r fertility_forwards`.
    - backward-counted: `r fertility_backwards`.
3. We can estimate fertility and know about an interaction with a man (unrelated): `r fertile_known_man_known_days` days.


# exclusion criteria in diary merged with diary_social_exclusion
```{r}

# for now, we don't care whether people were seen or thought about
diary_social_exclusion = diary %>%
  mutate(person = 
           if_else(is.na(social_life_saw_people),
                   if_else(is.na(social_life_thought_about), NA_character_, as.character(social_life_thought_about)),
                   if_else(is.na(social_life_thought_about), as.character(social_life_saw_people), 
                           paste0(social_life_saw_people, ",", social_life_thought_about))
                   )
           ) %>%
  separate_rows(person, sep = ",") %>%
  mutate(person = stringr::str_trim(person)) %>% 
  ungroup() %>%
  distinct() # brute way of ensu

# but we want to make a variable saying whether that person was seen or thought about or both
# dummy dataset seen
seen_exclusion = diary %>% select(session, social_life_saw_people, created_diary) %>%
  mutate(person = social_life_saw_people, person_seen = TRUE) %>%
  separate_rows(person, sep = ",") %>%
  mutate(person = stringr::str_trim(person)) %>% 
  ungroup() %>%
  select(session, person, created_diary, person_seen) %>%
  na.omit() %>% 
  distinct()

# dummy dataset thought about
thought_about_exclusion = diary %>% select(session, social_life_thought_about, created_diary, included_d) %>%
  mutate(person = social_life_thought_about, person_thought_about = TRUE) %>%
  separate_rows(person, sep = ",") %>%
  mutate(person = stringr::str_trim(person)) %>% 
  ungroup() %>%
  select(session, person, created_diary, person_thought_about) %>%
  na.omit() %>% 
  distinct()

# merge in
diary_social_exclusion = diary_social_exclusion %>% left_join(seen_exclusion, by = c("session", "person", "created_diary"))
diary_social_exclusion = diary_social_exclusion %>% left_join(thought_about_exclusion, by = c("session", "person", "created_diary"))
# crosstabs(~ person_seen + person_thought_about, diary_social_exclusion)

diary_social_exclusion %>% group_by(session, created_diary, person) %>% filter(n()>1) %>% nrow()

diary_social_exclusion = diary_social_exclusion %>% left_join(network, by = c("session", "short", "person")) %>% mutate(interaction_partner = paste0(short, "_", person))

nrow(diary_social_exclusion %>% filter(included_d == T & !is.na(fertile_fab)))
nrow(diary_social %>% filter(included_s == T & !is.na(fertile_fab)))
```

# Contraception
```{r}
library(UpSetR)
comma_separated_to_columns <- function(df, col) {
  colname <- deparse(substitute(col))
  df$splitcol <- df %>% pull(colname)
  separate_rows(df, splitcol, convert = TRUE, sep = ", ") %>% 
    mutate(splitcol = if_else(is.na(splitcol), "no", 
                        if_else(splitcol == "" | 
                                  splitcol %in% c(), "other", as.character(splitcol)))) %>% 
    mutate(#splitcol = stringr::str_c(colname, "_", splitcol), 
           value = 1) %>% 
    spread(splitcol, value, fill = 0) %>% 
    select(-colname)
}
library(UpSetR)
all_surveys %>% select(session, contraception_method) %>% 
  comma_separated_to_columns(contraception_method) %>% 
  select(-session) %>% 
  {
  upset(., ncol(.), 20, show.numbers = TRUE, order.by = "freq",
      main.bar.color = "#6E8691",
      matrix.color = "#6E8691",
      sets.bar.color = "#53AC9B")
  }

```

## social network 
```{r}
summary(as.factor(network$person_sex))
by_sex = s4_timespent %>% 
    group_by(session) %>% 
    summarise(female = sum(person_sex == 1, na.rm=T), male = sum(person_sex == 2, na.rm=T), n= n()) %>% select(female, male,n)
```


```{r}
total_network = nrow(network)
persons= nrow(network %>% filter(person_remember == 1 & !is.na(ended)))

```
__`r total_network`__ number of persons who were mentioned in diary
__`r persons`__ number of nicknames/names women remembered.


## Exclusion network

```{r}
source("0_helpers.R") 
network$included <- TRUE
excluded_old_network = 0


pipeline_network = list()
excluded_old_network = NULL
network = network %>% mutate(included = if_else(included, 
                                                !is.na(ended), F))

newly_excluded_network = sum( !network$included)

      
pipeline_network$not_remembered = n_excluded_network(network$included)



```

```{r}
network = network %>% mutate(included = if_else(included, 
                                                person_remember ==1, F))

newly_excluded_network = sum( !network$included)

      
pipeline_network$not_finished = n_excluded_network(network$included)

```
### strict exclusion 

```{r}
unique(network$person_sex_other)

``` 


```{r}


network$included_strict <- TRUE

pipeline_network_strict = list()
excluded_old_network_strict = NULL
network = network %>% mutate(included_strict = if_else(included_strict, 
                                                !is.na(ended), F))

newly_excluded_network_strict = sum( !network$included_strict)

      
pipeline_network$not_finished_strict = n_excluded_network_strict(network$included_strict)

```

```{r}

network = network %>% mutate(included_strict = if_else(included_strict, 
                                                person_remember == 1, F))

newly_excluded_network_strict = sum( !network$included_strict)

      
pipeline_network$not_remembered_strict = n_excluded_network_strict(network$included_strict)

```

```{r}

network = network %>% mutate(included_strict = if_else(included_strict, 
                                                person_age > 0, F))

newly_excluded_network_strict = sum( !network$included_strict)

      
pipeline_network$several_persons_strict = n_excluded_network_strict(network$included_strict)


```

```{r}
network = network %>% mutate(included_strict = if_else(included_strict, 
                                                person_sex != 3, F))

newly_excluded_network_strict = sum( !network$included_strict)

      
pipeline_network$several_persons_strict = n_excluded_network_strict(network$included_strict)


```


```{r}

person_excluded = nrow(network %>% filter(included == T))
person_excluded_strict = nrow(network %>% filter(included_strict == T))

``` 

__`r person_excluded`__ number of persons included after excluding incorrect information 
__`r person_excluded_strict`__ number of persons included after excluding incorrect information (strict)

# Save
```{r}
save(diary_social, diary, network_nominations, network, s1_demo, s1_filter, s2_initial, s3_daily, s4_followup, s4_timespent, withfollowup, all_surveys, file = "cleaned_selected.rdata")
``` 

## demographics final sample


```{r}

options(digits = 4)


all_surveys %>% 
  filter(included == T & hormonal_contraception == T) %>%
  select(age, religiosity, first_time, menstruation_length, number_sexual_partner, menarche, education_years) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  data.frame() %>% 
  pander()


```

```{r}
all_surveys %>% 
  filter(included == T & hormonal_contraception == F) %>%
  select(age, religiosity, first_time, menstruation_length, number_sexual_partner, menarche, education_years) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  pander()


```

age distribution
```{r}
ggplot(diary %>% filter(included_d==T & hormonal_contraception == T), aes(x = age), ) + geom_histogram(binwidth = 1) + xlab("Age")
```

```{r}

ggplot(diary %>% filter(included_d==T & hormonal_contraception == F), aes(x = age), ) + geom_histogram(binwidth = 1) + xlab("Age")
```


occupation

```{r}

bar_count(all_surveys %>% filter(included == T), occupational_status)

```

income
```{r}
bar_count(all_surveys %>% filter(included == T), net_income)
```



religion

```{r}
bar_count(all_surveys %>% filter(included == T), religion)
```


religiosity
```{r}

bar_count(all_surveys %>% filter(included == T), religiosity)
```

education
```{r}
bar_count(all_surveys %>% filter(included == T), education_level)

```



age at menarche
```{r}

ggplot(all_surveys %>% filter(included == T), aes(x = menarche), ) + geom_histogram(binwidth = 1) + xlab("Age at menarche")

```

children? 1=yes, 0 = no
```{r}
bar_count(all_surveys %>% filter(included == T), has_children)

```
pregnant trying 
1= trying to avoid it 
6= trying to get pregnant 
```{r}
bar_count(all_surveys %>% filter(included == T), pregnant_trying)

```

flat sharing? 
1= no 
2= with parents/grand-parents 
3= yes 
```{r}

bar_count(all_surveys %>% filter(included == T), abode_flat_share)

```


```{r}
ggplot(all_surveys %>% filter(included == T), aes(x = first_time), ) + geom_histogram(binwidth = 1) + xlab("Age at first time (sex)")

```

contraception at all
1 = yes 
2 = usually
3 = risk it 
4 = no 
5 = no sex 
6 = other reason

```{r}
bar_count(all_surveys %>% filter(included == T), contraception_at_all)

```

number sexual partner 
```{r}
ggplot(all_surveys %>% filter(included == T), aes(x = number_sexual_partner)) + geom_histogram(binwidth = 1) + xlab("Anzahl Sexualpartner")
```

### social network - demographics 

```{r}

options(digits = 4)


network %>%
  filter(included ==T) %>%
  select(person_age) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  data.frame() %>% 
  pander()


```

```{r}
options(digits = 4)


network %>%
  filter(included_strict ==T) %>%
  select(person_age) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  data.frame() %>% 
  pander()
```

```{r}
by_sex = network %>% 
    group_by(session) %>% 
    summarise(female = sum(person_sex == 1, na.rm=T), male = sum(person_sex == 2, na.rm=T), n= n()) %>% select(female, male,n)
```

```{r}

network %>% filter(included == T) %>% select(person_sex) %>% mutate(person_sex = factor(person_sex, levels=c(1,2,3))) %>% summary()
network %>% filter(included_strict == T) %>% select(person_sex) %>% mutate(person_sex = factor(person_sex, levels=c(1,2,3))) %>% summary()


# network %>% filter(included == T & is.na(person_sex)) %>% View()
```


```{r}

bar_count(network %>% filter (included == T), person_relationship_to_anchor)

bar_count(network %>% filter (included_strict == T), person_relationship_to_anchor)

```

```{r}

bar_count(network %>% filter(included == T), person_relationship_status)
bar_count(network %>% filter(included_strict == T), person_relationship_status)
```

```{r}
bar_count(network %>% filter(included == T & !is.na(kinship_cleaned)), kinship_cleaned)

```

romantic experience? only asked if person is not related and male 
```{r}

bar_count(network %>% filter(included == T & person_sex==2 & person_relationship_to_anchor !='biological_relative'), person_romantic_experience)

``` 


## No missings in included variables?
```{r}
crosstabs(~ all_surveys$included)
crosstabs(~ diary$included_d)
crosstabs(~ diary_social$included_s)
crosstabs(~ network$included)
```



