# Alltag und Sex - Descriptives {.tabset .tabset-sticky}

```{r}
source("0_helpers.R")
load("data/cleaned_selected.rdata")
opts_chunk$set(warning = F, message = F, error = T)

library(knitr)
opts_chunk$set(fig.width = 9, fig.height = 7, cache = T, warning = F, message = F, cache = F, error = T)
```

## Who completed what? {.tabset .tabset-sticky}

### Participant funnel

```{r}
began_s1_demo = sum(!is.na(s1_demo$created))
ended_s1_demo = sum(!is.na(s1_demo$ended))
diary <- s1_filter %>% left_join(diary, by = c('session', 'short'), suffix = c("_filter", ""))
ended_pre = diary %>% filter(!is.na(ended_initial)) %>% ungroup() %>% summarise(n = n_distinct(session)) %>% pull(n)
diary %>% group_by(gets_paid) %>% summarise(n = sum(!is.na(ended_initial[!duplicated(session)]), n = n_distinct(session)))
at_least_one_diary_entry = diary %>% group_by(session) %>% summarise(n = n_nonmissing(ended_diary)) %>% filter(n >= 1) %>% nrow()
at_least_20_diary_entries = diary %>% group_by(session) %>% summarise(n = n_nonmissing(ended_diary)) %>% filter(n >= 20) %>% nrow()
at_least_50_diary_entries = diary %>% group_by(session) %>% summarise(n = n_nonmissing(ended_diary)) %>% filter(n >= 50) %>% nrow()

in_relationship = sum(s1_demo$hetero_relationship, na.rm = T)
singles = sum(! s1_demo$hetero_relationship, na.rm = T)

at_least_one_diary_entry = s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 1) %>% nrow()
at_least_20_diary_entries = s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 20) %>% nrow()
at_least_50_diary_entries = s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 50) %>% nrow()

mean_diary_entries <- s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% summarise(mean(n))

mean_diary_entries_by_payment <- s1_filter %>% 
  select(-ended) %>% left_join(s3_daily, by = 'session') %>% 
  group_by(gets_paid, session) %>%
  summarise(n = n_nonmissing(ended)) %>% 
  filter(n > 0) %>% 
  group_by(gets_paid) %>% 
  summarise(responses = mean(n), n = n_distinct(session))

response_rate_over_time <- diary %>% filter(day_number > 0, day_number < 70) %>% 
    left_join(s1_filter, by = 'session', suffix = c("", "_filter")) %>% 
  left_join(mean_diary_entries_by_payment) %>% 
  group_by(gets_paid, day_number) %>% 
  summarise(entries = n_nonmissing(ended_diary),
            rr = entries / unique(n))
ggplot(response_rate_over_time, aes(day_number, rr, colour = gets_paid)) + geom_point() +
    ggtitle("Response rate over time", "for people who started the diary") + ylim(0,1)

mean_diary_entries_finishers <- s4_followup %>% select(-ended) %>% left_join(s3_daily, by = 'session') %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% summarise(mean(n))

response_rate_over_time <- s4_followup %>% select(-ended) %>% 
  left_join(diary %>% select(session, day_number, created_diary, ended_diary)) %>% filter(day_number > 0, day_number < 70) %>% 
  left_join(s1_filter, by = 'session', suffix = c("", "_filter")) %>% 
  left_join(mean_diary_entries_by_payment) %>% 
  group_by(gets_paid, day_number) %>% 
  summarise(entries = n_nonmissing(ended_diary),
            rr = entries / unique(n))
ggplot(response_rate_over_time, aes(day_number, rr, colour = gets_paid)) + 
  geom_point() +
    ggtitle("Response rate over time", "for people who finished the diary") + ylim(0,1)

nsmt2d_over_time <- s4_followup %>% select(-ended) %>% 
  left_join(diary %>% select(session, day_number, never_skipped_more_than_2, created_diary, ended_diary)) %>% 
  left_join(s1_filter, by = 'session', suffix = c("", "_filter")) %>% 
  left_join(mean_diary_entries_by_payment) %>% 
  group_by(gets_paid, day_number) %>% 
  summarise(entries = sum(as.numeric(never_skipped_more_than_2), na.rm = T),
            rr = entries / unique(n))

ggplot(nsmt2d_over_time, aes(day_number, rr, colour = gets_paid)) + 
  geom_point() +
    ggtitle("Percentage who never skipped more than two days over time", "for people who finished the diary") + ylim(0,1)


mean_finishing_personality_by_payment <- s1_demo %>% 
  left_join(s1_filter, by = 'session', suffix = c("_demo", "")) %>% 
  left_join(s2_initial,by ='session', suffix = c("", "_initial")) %>% 
  group_by(gets_paid) %>% 
  summarise(finish_demo = n_nonmissing(ended_demo), 
            finish_initial = n_nonmissing(ended_initial), n = n(),
            prc_ini_over_demo = round(100*finish_initial/finish_demo),
            consc = mean(bfi_consc,na.rm=T))
kable(mean_finishing_personality_by_payment)

mean_finishing_follow_up_by_payment <- s1_filter %>% select(-ended) %>% right_join(s2_initial,by ='session') %>% left_join(s4_followup, by = 'session', suffix = c("_initial", "_followup")) %>% group_by(gets_paid) %>% summarise(followup = n_nonmissing(ended_followup), initial = n_nonmissing(ended_initial), n(), prc_fu_over_initial = round(100*followup/initial))
kable(mean_finishing_follow_up_by_payment)

fertile_known_man_known = diary_social %>% group_by(session, created) %>% 
  summarise(n = n_nonmissing(person_attractiveness_short_term)) %>% 
  group_by(session) %>% summarise(n = sum(n)) # fertility known, man known
fertile_known_man_known$n %>% qplot() + xlim(1,NA)

fertile_known_person_known = diary_social %>% group_by(session, created) %>% 
  summarise(n = n_nonmissing(person_sex)) %>% 
  group_by(session) %>% summarise(n = sum(n)) # fertility known, man known

finished_timespent = s4_timespent %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 1) %>% nrow()
timespent_gt3 = s4_timespent %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n > 3) %>% nrow()
timespent_men = network %>% group_by(session) %>% filter(person_sex == 2, person_relationship_to_anchor != "biological_relative") %>% summarise(n = n_nonmissing(ended)) %>% filter(n > 0) %>% nrow()
timespent_3men = network %>% group_by(session) %>% filter(person_sex == 2, person_relationship_to_anchor != "biological_relative") %>% summarise(n = n_nonmissing(ended)) %>% filter(n > 2) %>% nrow()

fertile_known_man_known_participants = fertile_known_man_known %>% filter(n > 0) %>% nrow()
fertile_known_person_known_participants = fertile_known_person_known %>% filter(n > 0) %>% nrow()

finished_followup = sum(!is.na(s4_followup$ended))

# all_surveys %>% mutate(
#   should_be_done = created_demo + days(70) < today()
# ) %>% filter(should_be_done == T) %>% xtabs(~ is.na(ended), .)

# all_surveys %>% mutate(
# should_be_done = created_demo + days(70) < today()
# ) %>% left_join(s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended))) %>% 
#  filter(should_be_done == T, n > 40) %>% xtabs(~ is.na(ended), .)

all_surveys %>% mutate(should_be_done = created_demo + days(70) < today()) %>%
 left_join( s4_timespent %>% group_by(session) %>% summarise(n_timespent = n_nonmissing(ended)), by = 'session') %>% 
 filter(hetero_relationship == 0, should_be_done == T, n_timespent > 0, !is.na(n_timespent)) %>% nrow()

all_surveys %>% mutate(should_be_done = created_demo + days(70) < today()) %>%
 left_join( s4_timespent %>% group_by(session) %>% summarise(n_timespent =  n_nonmissing(ended)), by = 'session') %>% 
 filter(hetero_relationship == 0 & should_be_done == T & (is.na(n_timespent) | n_timespent == 0)) %>% nrow()
```

1. __`r began_s1_demo`__ signed up for the study.
2. __`r ended_s1_demo`__ finished the demographics (`r singles` singles, `r in_relationship` in relationship).
2. __`r ended_pre`__ finished the demographic and personality questionnaires.
3. __`r at_least_one_diary_entry`__ submitted at least one diary entry (>= 20: `r at_least_20_diary_entries`, >= 50 `r at_least_50_diary_entries`). On average participants completed `r mean_diary_entries` diary entries.
4. `r finished_timespent` singles reported information on least one person mentioned during the diary (>3: `r timespent_gt3`, at least one man who wasn't biologically related: `r timespent_men`, >2men: `r timespent_3men`). 
5. __`r finished_followup`__ (`r round(100*finished_followup/ended_pre)`% of those who finished the intake survey) finished the follow-up survey. Finishers completed on average `r mean_diary_entries_finishers` diary entries.




# Contraception
```{r}
library(UpSetR)
comma_separated_to_columns <- function(df, col) {
  colname <- deparse(substitute(col))
  df$splitcol <- df %>% pull(colname)
  separate_rows(df, splitcol, convert = TRUE, sep = ", ") %>% 
    mutate(splitcol = if_else(is.na(splitcol), "no", 
                        if_else(splitcol == "" | 
                                  splitcol %in% c(), "other", as.character(splitcol)))) %>% 
    mutate(#splitcol = stringr::str_c(colname, "_", splitcol), 
           value = 1) %>% 
    spread(splitcol, value, fill = 0) %>% 
    select(-colname)
}
library(UpSetR)
all_surveys %>% select(session, contraception_method) %>% 
  comma_separated_to_columns(contraception_method) %>% 
  select(-session) %>% 
  {
  upset(., ncol(.), 20, show.numbers = TRUE, order.by = "freq",
      main.bar.color = "#6E8691",
      matrix.color = "#6E8691",
      sets.bar.color = "#53AC9B")
  }

```

## social network 
```{r}
summary(as.factor(network$person_sex))
by_sex = s4_timespent %>% 
    group_by(session) %>% 
    summarise(female = sum(person_sex == 1, na.rm=T), male = sum(person_sex == 2, na.rm=T), n= n()) %>% select(female, male,n)
```


```{r}
total_network = nrow(network)
persons= nrow(network %>% filter(person_remember == 1 & !is.na(ended)))

```
__`r total_network`__ number of persons who were mentioned in diary
__`r persons`__ number of nicknames/names women remembered.

## demographics final sample


```{r}

options(digits = 4)


all_surveys %>% 
  filter(reasons_for_exclusion == "" & hormonal_contraception == T) %>%
  select(age, religiosity, first_time, menstruation_length, number_sexual_partner, menarche, education_years) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  data.frame() %>% 
  pander()


```

```{r}
all_surveys %>% 
  filter(reasons_for_exclusion == "" & hormonal_contraception == F) %>%
  select(age, religiosity, first_time, menstruation_length, number_sexual_partner, menarche, education_years) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  pander()


```

age distribution
```{r}
ggplot(diary %>% filter(included_d==T & hormonal_contraception == T), aes(x = age), ) + geom_histogram(binwidth = 1) + xlab("Age")
```

```{r}

ggplot(diary %>% filter(included_d==T & hormonal_contraception == F), aes(x = age), ) + geom_histogram(binwidth = 1) + xlab("Age")
```


occupation

```{r}

bar_count(all_surveys %>% filter(reasons_for_exclusion == ""), occupational_status)

```

income
```{r}
bar_count(all_surveys %>% filter(reasons_for_exclusion == ""), net_income)
```



religion

```{r}
bar_count(all_surveys %>% filter(reasons_for_exclusion == ""), religion)
```


religiosity
```{r}

bar_count(all_surveys %>% filter(reasons_for_exclusion == ""), religiosity)
```

education
```{r}
bar_count(all_surveys %>% filter(reasons_for_exclusion == ""), education_level)

```



age at menarche
```{r}

ggplot(all_surveys %>% filter(reasons_for_exclusion == ""), aes(x = menarche), ) + geom_histogram(binwidth = 1) + xlab("Age at menarche")

```

children? 1=yes, 0 = no
```{r}
bar_count(all_surveys %>% filter(reasons_for_exclusion == ""), has_children)

```
pregnant trying 
1= trying to avoid it 
6= trying to get pregnant 
```{r}
bar_count(all_surveys %>% filter(reasons_for_exclusion == ""), pregnant_trying)

```

flat sharing? 
1= no 
2= with parents/grand-parents 
3= yes 
```{r}

bar_count(all_surveys %>% filter(reasons_for_exclusion == ""), abode_flat_share)

```


```{r}
ggplot(all_surveys %>% filter(reasons_for_exclusion == ""), aes(x = first_time), ) + geom_histogram(binwidth = 1) + xlab("Age at first time (sex)")

```

contraception at all
1 = yes 
2 = usually
3 = risk it 
4 = no 
5 = no sex 
6 = other reason

```{r}
bar_count(all_surveys %>% filter(reasons_for_exclusion == ""), contraception_at_all)

```

number sexual partner 
```{r}
ggplot(all_surveys %>% filter(reasons_for_exclusion == ""), aes(x = number_sexual_partner)) + geom_histogram(binwidth = 1) + xlab("Anzahl Sexualpartner")
```

### social network - demographics 

```{r}

options(digits = 4)


network %>%
  filter(included ==T) %>%
  select(person_age) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  data.frame() %>% 
  pander()


```

```{r}
options(digits = 4)


network %>%
  filter(included_strict ==T) %>%
  select(person_age) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  data.frame() %>% 
  pander()
```

```{r}
by_sex = network %>% 
    group_by(session) %>% 
    summarise(female = sum(person_sex == 1, na.rm=T), male = sum(person_sex == 2, na.rm=T), n= n()) %>% select(female, male,n)
```

```{r}

network %>% filter(reasons_for_exclusion == "") %>% select(person_sex) %>% mutate(person_sex = factor(person_sex, levels=c(1,2,3))) %>% summary()
network %>% filter(included_strict == T) %>% select(person_sex) %>% mutate(person_sex = factor(person_sex, levels=c(1,2,3))) %>% summary()


# network %>% filter(reasons_for_exclusion == "" & is.na(person_sex)) %>% View()
```


```{r}

bar_count(network %>% filter (reasons_for_exclusion == ""), person_relationship_to_anchor)

bar_count(network %>% filter (included_strict == T), person_relationship_to_anchor)

```

```{r}

bar_count(network %>% filter(reasons_for_exclusion == ""), person_relationship_status)
bar_count(network %>% filter(included_strict == T), person_relationship_status)
```

```{r}
bar_count(network %>% filter(reasons_for_exclusion == "" & !is.na(kinship_cleaned)), kinship_cleaned)

```

romantic experience? only asked if person is not related and male 
```{r}

bar_count(network %>% filter(reasons_for_exclusion == "" & person_sex==2 & person_relationship_to_anchor !='biological_relative'), person_romantic_experience)

``` 


## No missings in included variables?
```{r}
crosstabs(~ all_surveys$included)
crosstabs(~ diary$included_d)
crosstabs(~ diary_social$included_s)
crosstabs(~ network$included)
```

### Response rates and dropout

```{r}
began_s1_demo = sum(!is.na(s1_demo$created))
ended_s1_demo = sum(!is.na(s1_demo$ended))
diary <- diary %>% left_join(s1_filter, by = c('session', 'short'), suffix = c("", "_filter"))
ended_pre = diary %>% filter(!is.na(ended_initial)) %>% ungroup() %>% summarise(n = n_distinct(session)) %>% pull(n)
diary %>% group_by(gets_paid) %>% summarise(n = sum(!is.na(ended_initial[!duplicated(session)]), n = n_distinct(session)))
at_least_one_diary_entry = diary %>% group_by(session) %>% summarise(n = n_nonmissing(ended_diary)) %>% filter(n >= 1) %>% nrow()
at_least_20_diary_entries = diary %>% group_by(session) %>% summarise(n = n_nonmissing(ended_diary)) %>% filter(n >= 20) %>% nrow()
at_least_50_diary_entries = diary %>% group_by(session) %>% summarise(n = n_nonmissing(ended_diary)) %>% filter(n >= 50) %>% nrow()

in_relationship = sum(s1_demo$hetero_relationship, na.rm = T)
singles = sum(! s1_demo$hetero_relationship, na.rm = T)

at_least_one_diary_entry = s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 1) %>% nrow()
at_least_20_diary_entries = s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 20) %>% nrow()
at_least_50_diary_entries = s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 50) %>% nrow()

mean_diary_entries <- s3_daily %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% summarise(mean(n))

mean_diary_entries_by_payment <- s1_filter %>% 
  select(-ended) %>% left_join(s3_daily, by = 'session') %>% 
  group_by(gets_paid, session) %>%
  summarise(n = n_nonmissing(ended)) %>% 
  filter(n > 0) %>% 
  group_by(gets_paid) %>% 
  summarise(responses = mean(n), n = n_distinct(session))

response_rate_over_time <- diary %>% filter(day_number > 0, day_number < 70) %>% 
    left_join(s1_filter, by = 'session', suffix = c("", "_filter")) %>% 
  left_join(mean_diary_entries_by_payment) %>% 
  group_by(gets_paid, day_number) %>% 
  summarise(entries = n_nonmissing(ended_diary),
            rr = entries / unique(n))
ggplot(response_rate_over_time, aes(day_number, rr, colour = gets_paid)) + geom_point() +
    ggtitle("Response rate over time", "for people who started the diary")



response_rate_over_time <- diary %>% filter(day_number > 0, day_number < 70) %>% 
  filter(reasons_for_exclusion == "") %>% 
    left_join(s1_filter, by = 'session', suffix = c("", "_filter")) %>% 
  left_join(mean_diary_entries_by_payment) %>% 
  group_by(gets_paid, day_number) %>% 
  summarise(entries = n_nonmissing(ended_diary),
            rr = entries / unique(n))
ggplot(response_rate_over_time, aes(day_number, rr, colour = gets_paid)) + geom_point() +
    ggtitle("Response rate over time", "for included subsample")

mean_diary_entries_finishers <- s4_followup %>% select(-ended) %>% left_join(s3_daily, by = 'session') %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% summarise(mean(n))

response_rate_over_time <- s4_followup %>% select(-ended) %>% 
  left_join(diary %>% select(session, day_number, created_diary, ended_diary)) %>% filter(day_number > 0, day_number < 70) %>% 
  left_join(s1_filter, by = 'session', suffix = c("", "_filter")) %>% 
  left_join(mean_diary_entries_by_payment) %>% 
  group_by(gets_paid, day_number) %>% 
  summarise(entries = n_nonmissing(ended_diary),
            rr = entries / unique(n))
ggplot(response_rate_over_time, aes(day_number, rr, colour = gets_paid)) + 
  geom_point() +
    ggtitle("Response rate over time", "for people who finished the diary")

nsmt2d_over_time <- s4_followup %>% select(-ended) %>% 
  left_join(diary %>% select(session, day_number, never_skipped_more_than_2, created_diary, ended_diary)) %>% filter(day_number > 0, day_number < 70) %>% 
  left_join(s1_filter, by = 'session', suffix = c("", "_filter")) %>% 
  left_join(mean_diary_entries_by_payment) %>% 
  group_by(gets_paid, day_number) %>% 
  summarise(entries = sum(as.numeric(never_skipped_more_than_2)),
            rr = entries / unique(n))

ggplot(nsmt2d_over_time, aes(day_number, rr, colour = gets_paid)) + 
  geom_point() +
    ggtitle("Percentage who never skipped more than two days over time", "for people who finished the diary")


mean_finishing_personality_by_payment <- s1_demo %>% 
  left_join(s1_filter, by = 'session', suffix = c("_demo", "")) %>% 
  left_join(s2_initial,by ='session', suffix = c("", "_initial")) %>% 
  group_by(gets_paid) %>% 
  summarise(finish_demo = n_nonmissing(ended_demo), 
            finish_initial = n_nonmissing(ended_initial), n = n(),
            prc_ini_over_demo = round(100*finish_initial/finish_demo),
            consc = mean(bfi_consc,na.rm=T))
kable(mean_finishing_personality_by_payment)

mean_finishing_follow_up_by_payment <- s1_filter %>% select(-ended) %>% right_join(s2_initial,by ='session') %>% left_join(s4_followup, by = 'session', suffix = c("_initial", "_followup")) %>% group_by(gets_paid) %>% summarise(followup = n_nonmissing(ended_followup), initial = n_nonmissing(ended_initial), n(), prc_fu_over_initial = round(100*followup/initial))
kable(mean_finishing_follow_up_by_payment)

fertile_known_man_known = diary_social %>% group_by(session, created) %>% 
  summarise(n = n_nonmissing(person_attractiveness_short_term)) %>% 
  group_by(session) %>% summarise(n = sum(n)) # fertility known, man known
fertile_known_man_known$n %>% qplot() + xlim(1,NA)

fertile_known_person_known = diary_social %>% group_by(session, created) %>% 
  summarise(n = n_nonmissing(person_sex)) %>% 
  group_by(session) %>% summarise(n = sum(n)) # fertility known, man known

finished_timespent = s4_timespent %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n >= 1) %>% nrow()
timespent_gt3 = s4_timespent %>% group_by(session) %>% summarise(n = n_nonmissing(ended)) %>% filter(n > 3) %>% nrow()
timespent_men = network %>% group_by(session) %>% filter(person_sex == 2, person_relationship_to_anchor != "biological_relative") %>% summarise(n = n_nonmissing(ended)) %>% filter(n > 0) %>% nrow()
timespent_3men = network %>% group_by(session) %>% filter(person_sex == 2, person_relationship_to_anchor != "biological_relative") %>% summarise(n = n_nonmissing(ended)) %>% filter(n > 2) %>% nrow()

fertile_known_man_known_participants = fertile_known_man_known %>% filter(n > 0) %>% nrow()
fertile_known_person_known_participants = fertile_known_person_known %>% filter(n > 0) %>% nrow()

finished_followup = sum(!is.na(s4_followup$ended))

all_surveys %>% mutate(should_be_done = created_demo + days(70) < today()) %>%
 left_join( s4_timespent %>% group_by(session) %>% summarise(n_timespent = n_nonmissing(ended)), by = 'session') %>% 
 filter(hetero_relationship == 0, should_be_done == T, n_timespent > 0, !is.na(n_timespent)) %>% nrow()

all_surveys %>% mutate(should_be_done = created_demo + days(70) < today()) %>%
 left_join( s4_timespent %>% group_by(session) %>% summarise(n_timespent =  n_nonmissing(ended)), by = 'session') %>% 
 filter(hetero_relationship == 0 & should_be_done == T & (is.na(n_timespent) | n_timespent == 0)) %>% nrow()
```

1. __`r began_s1_demo`__ signed up for the study.
2. __`r ended_s1_demo`__ finished the demographics (`r singles` singles, `r in_relationship` in relationship).
2. __`r ended_pre`__ finished the demographic and personality questionnaires.
3. __`r at_least_one_diary_entry`__ submitted at least one diary entry (>= 20: `r at_least_20_diary_entries`, >= 50 `r at_least_50_diary_entries`). On average participants completed `r mean_diary_entries` diary entries.
4. `r finished_timespent` singles reported information on least one person mentioned during the diary (>3: `r timespent_gt3`, at least one man who wasn't biologically related: `r timespent_men`, >2men: `r timespent_3men`). 
5. __`r finished_followup`__ (`r round(100*finished_followup/ended_pre)`% of those who finished the intake survey) finished the follow-up survey. Finishers completed on average `r mean_diary_entries_finishers` diary entries.



