# Reasons for Exclusion 

```{r}
source("0_helpers.R")
library(tidylog)
load("data/cleaned.rdata")

library(knitr)
opts_chunk$set(fig.width = 9, fig.height = 7, cache = T, warning = T, message = T, cache = F, error = FALSE)

comma_separated_to_columns <- function(df, col) {
  colname <- deparse(substitute(col))
  df$splitcol <- df %>% pull(colname)
  separate_rows(df, splitcol, convert = TRUE, sep = ", ") %>% 
    mutate(splitcol = if_else(is.na(splitcol), "no", 
                        if_else(splitcol == "" | 
                                  splitcol %in% c(), "included", as.character(splitcol)))) %>% 
    mutate(#splitcol = stringr::str_c(colname, "_", splitcol), 
           value = 1) %>% 
    spread(splitcol, value, fill = 0) %>% 
    select(-colname)
}

all_survey_length <- nrow(all_surveys)
diary_length <- nrow(diary)
diary_social_length <- nrow(diary_social)
```

```{r}
diary$reasons_for_exclusion_diary <- ""
```


Lab participants that did not do the online diary (not merged)

```{r}
diary <- diary %>% 
  mutate(reasons_for_exclusion_diary = str_c(reasons_for_exclusion_diary,
                                            if_else(is.na(session), "lab_only, ", "", "")
                                       )
  )
```

Disclosed that they responded dishonestly on that day.

```{r}
diary <- diary %>% 
  mutate(reasons_for_exclusion_diary = str_c(reasons_for_exclusion_diary,
                                            if_else(dishonest_discard == 1, "dishonest_answer, ", "", "")
                                       )
  )
```

Did not finish diary entry.

```{r}
diary <- diary %>% 
  mutate(reasons_for_exclusion_diary = str_c(reasons_for_exclusion_diary,
                                            if_else(is.na(ended_diary) & !is.na(modified_diary), "did_not_finish_entry, ", "", "")
                                       )
  )
```


Cycle shorter than 20 days.
```{r}
diary <- diary %>% 
  mutate(reasons_for_exclusion_diary = str_c(reasons_for_exclusion_diary,
                                            if_else(coalesce(minimum_cycle_length_diary, as.numeric(menstruation_length)) < 20, "cycle_shorter_than_20, ", "", "")
                                       )
  )
```

Cycle longer than 40 days.
```{r}
diary <- diary %>% 
  mutate(reasons_for_exclusion_diary = str_c(reasons_for_exclusion_diary,
                                            if_else(coalesce(minimum_cycle_length_diary, as.numeric(menstruation_length)) > 40, "cycle_longer_than_40, ", "", "")
                                       )
  )
```

Next menstrual onset not observed

```{r}
diary <- diary %>% 
  mutate(reasons_for_exclusion_diary = str_c(reasons_for_exclusion_diary,
                                            if_else(
                                              menstruation_regular == 1 &
                                              coalesce(minimum_cycle_length_diary, as.numeric(menstruation_length)) <= 40 &
                                              coalesce(minimum_cycle_length_diary, as.numeric(menstruation_length)) >= 20 &
                                              is.na(fertile_fab), "next_menstrual_onset_unobserved, ", "", "")
                                       )
  )
```


Skipped this diary day (days after dropping out not included)
```{r}
diary <- diary %>% 
  mutate(reasons_for_exclusion_diary = str_c(reasons_for_exclusion_diary,
                                            if_else(is.na(ended_diary) & is.na(modified_diary), "skipped_diary_entry, ", "")
                                       )
  )
```

```{r}
usable_diary_days <- diary %>% group_by(session) %>% 
  summarise(usable_diary_days = any(reasons_for_exclusion_diary == ""))
```



## Who completed what?

We create a character variable `reasons_for_exclusion`. We will concatenate (abbreviated)
reasons for exclusion in this variable.

```{r}
all_surveys$reasons_for_exclusion <- ""
```


Did not finish demographics survey
```{r}
all_surveys <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(is.na(ended_demo), "didnt_finish_demographics, ", "")
                                       )
  )
```


Reported no regular menstruation
```{r}
all_surveys <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(menstruation_regular == 0, "no_regular_menstruation, ", "", "")
                                       )
  )
```


Menopausal or in climacteric period
```{r}
all_surveys <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(menopause_yes == 1 | menopause_yes == 2, "menopausal, ", "", "")
                                       )
  )
```

Older than 50
```{r}
all_surveys <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(age >= 50, "older_than_50, ", "", "")
                                       )
  )
```

Pregnant
```{r}
all_surveys <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(pregnant == 1, "pregnant, ", "", "")
                                       )
  )
```

Breast-feeding
```{r}
all_surveys <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(breast_feeding == 1, "breast_feeding, ", "", "")
                                       )
  )
```


Not primarily heterosexual. This excludes women who reported being equally interested in men and women, women who reported being asexual or aromantic, and participants who did not identify as female gender.
```{r}
all_surveys <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(sex_orientation >= 4 | gender != 1, "not_heterosexual_female, ", "", "")
                                       )
  )
```

Did not finish personality survey
```{r}
all_surveys <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(!is.na(ended_demo) & is.na(ended_initial), "didnt_finish_personality, ", "")
                                       )
  )
```

Changed contraception
```{r}
all_surveys <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(change_to_nonhormonal != 0 | change_to_hormonal_contraception != 0, "switched_contraception, ", "", "")
                                       )
  )

```


Taking sex hormones (other than the pill)
```{r}
all_surveys <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(medication_name %contains% "Cycloprognova" |
                                                      medication_name %contains% "Cyproderm" |
                                                       medication_name %contains% "DHEA" |
                                                       medication_name %contains% "Hormone" |
                                                       medication_name %contains% "Cyclo-Progynova" |
                                                       medication_name %contains% "Femoston" |
                                                       medication_name %contains% "Gynokadin", "sex_hormones, ", "", "")
                                       )
  )

```

No diary days
```{r}
all_surveys <- all_surveys %>% 
  left_join(diary %>% group_by(session) %>% summarise(diary_days = n_nonmissing(ended_diary)), by = 'session') %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(!is.na(ended_initial) & diary_days == 0, "didnt_do_diary, ", "", "didnt_do_diary, ")
                                       )
  )
```

Fertility never estimable
```{r}
all_surveys <- all_surveys %>% 
  left_join(diary %>% group_by(session) %>% summarise(fertility_days = n_nonmissing(fertile_fab)), by = 'session') %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(menstruation_regular != 0  & diary_days > 0 & fertility_days == 0, 
                                                    "fertility_never_estimable, ", "", "")
                                       )
  )
```


```{r}
all_surveys <- all_surveys %>% left_join(usable_diary_days, by = "session") %>% 
    mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
            if_else(menstruation_regular != 0  & diary_days > 0 & fertility_days > 0 & !usable_diary_days, "diary_days_not_usable, ", "", "")
                                       )
  )
```

Women who are in monogamous heterosexual relationships
```{r}
all_surveys <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion,
                                            if_else(hetero_relationship == 0 & relationship_status != 1, "non_heterosexual_relationship, ", "", "")
                                       )
  )
```

## Reasons for exclusion

How to read this plot: The horizontal green bars show for how many women this reason for
exclusion applies. The blue bars show how many women are excluded for multiple reasons (e.g.,
they're menopausal _and_ not heterosexual). If reasons for exclusion necessarily depend on
another (i.e. participants had to finish the first survey to get to the second), we counted
only those who had not yet been excluded earlier. If reasons for exclusion depended on each
other only stochastically (e.g., age and menopause), we did not do this.

```{r}
testthat::expect_equal(all_surveys %>% group_by(session) %>% filter(n() > 1) %>% nrow(),
                       0)
table(all_surveys$reasons_for_exclusion == "", exclude = NULL)

library(UpSetR)
exclusion_reasons <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_sub(reasons_for_exclusion, 1, -3)) %>% 
  select(session, reasons_for_exclusion) %>% 
  comma_separated_to_columns(reasons_for_exclusion) %>% 
  select(-session)

exclusion_reasons %>% 
  summarise_all(sum) %>% sort() %>% 
  gather(reason, n) %>% 
  left_join(all_surveys %>% mutate(reason = str_sub(reasons_for_exclusion, 1, -3)) %>% group_by(reason) %>% summarise(unique = n())) %>% 
  mutate(unique = if_else(is.na(unique), 0L, unique)) %>% 
  knitr::kable()

exclusion_reasons %>% 
  filter(included == 0) %>% 
  select(-included) %>% 
  as.data.frame() %>% 
  {
  upset(., ncol(.), 20, show.numbers = TRUE, order.by = "freq",
      main.bar.color = "#6E8691",
      matrix.color = "#6E8691",
      sets.bar.color = "#53AC9B")
  }
```

### By contraception
```{r}
library(UpSetR)
exclusion_reasons_hc <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_sub(reasons_for_exclusion, 1, -3)) %>% 
  select(session, hormonal_contraception, reasons_for_exclusion) %>% 
  mutate(hormonal_contraception = if_else(hormonal_contraception, 1, 0)) %>% 
  comma_separated_to_columns(reasons_for_exclusion) %>% 
  # filter(included == 0) %>%
  select(-session)

exclusion_reasons_hc %>% group_by(hormonal_contraception) %>% 
  summarise_all(sum) %>% gather(reason, n, -hormonal_contraception) %>% 
  spread(hormonal_contraception, n) %>% 
  arrange(`0`) %>% knitr::kable()

exclusion_reasons_hc %>% 
  as.data.frame() %>% 
  {
  upset(., ncol(.), 20, show.numbers = TRUE, order.by = "freq",
      main.bar.color = "#6E8691",
      matrix.color = "#6E8691",
      sets.bar.color = "#53AC9B")
  }
```


## In the diary
```{r}
diary <- diary %>% left_join(all_surveys %>% select(session, reasons_for_exclusion), by = 'session') %>% 
  mutate(reasons_for_exclusion = str_c(reasons_for_exclusion, reasons_for_exclusion_diary))
```

```{r}
library(UpSetR)
exclusion_reasons_diary <- diary %>% 
  mutate(reasons_for_exclusion = str_sub(reasons_for_exclusion, 1, -3)) %>% 
  select(session, created_date, reasons_for_exclusion) %>% 
  drop_na(session, created_date) %>% 
  comma_separated_to_columns(reasons_for_exclusion) %>% 
  select( -created_date)

exclusion_reasons_diary %>% 
  select(-session) %>% 
  summarise_all(sum) %>% 
  sort() %>% 
  gather(reason, n) %>% 
  left_join(diary %>% mutate(reason = str_sub(reasons_for_exclusion, 1, -3)) %>% group_by(reason) %>% summarise(unique = n())) %>% 
  mutate(unique = if_else(is.na(unique), 0L, unique)) %>% 
  left_join(exclusion_reasons_diary %>% 
  gather(reason, n, -session) %>% 
  filter(n > 0) %>% 
  distinct(session, reason, n) %>% 
  group_by(reason) %>%
  summarise(n_women = sum(n))) %>% 
  knitr::kable()


exclusion_reasons_diary %>% 
  filter(included == 0) %>%
  select(-session, -included, -didnt_do_diary) %>% 
  as.data.frame() %>% 
  {
  upset(., ncol(.), 20, show.numbers = TRUE, order.by = "freq",
      main.bar.color = "#6E8691",
      matrix.color = "#6E8691",
      sets.bar.color = "#53AC9B")
  }

included <- diary %>% filter(reasons_for_exclusion == "") %>% distinct(session)

testthat::expect_equal(
  all_surveys %>% filter(reasons_for_exclusion == "") %>% nrow(), 
  nrow(included)
)
```


# Sanity Checks
```{r}
library(testthat)
expect_equal(nrow(diary), diary_length)
expect_equal(nrow(all_surveys), all_survey_length)
expect_equal(nrow(diary_social), diary_social_length)
expect_false(any(names(diary) %contains% ".x"))
expect_false(any(names(diary) %contains% ".y"))
expect_false(any(names(all_surveys) %contains% ".y"))
expect_equal(groups(s3_daily), list())
expect_equal(groups(diary), list())
expect_equal(groups(all_surveys), list())
expect_equal(sum(duplicated(all_surveys$session)), 0)
expect_equal(sum(duplicated(s1_demo$session)), 0)
expect_equal(diary %>% drop_na(session, day_number) %>% 
               group_by(short, day_number) %>% filter(n() > 1) %>% nrow(), 0)
expect_equal(diary %>% drop_na(session, created_diary) %>%  
            group_by(session, created_diary) %>% filter(n()>1) %>% nrow(), 0)
expect_equal(s3_daily %>% drop_na(session, created_date) %>%  
            group_by(session, created_date) %>% filter(n()>1) %>% nrow(), 0)
expect_equal(diary %>% drop_na(session, created_date) %>%  
            group_by(session, created_date) %>% filter(n()>1) %>% nrow(), 0)
expect_equal(diary_social %>% drop_na(session, created_diary, person) %>%  
            group_by(session, created_diary, person) %>% filter(n() > 1) %>% nrow(), 0)
expect_equal(network %>% drop_na(session, person) %>%  
            group_by(session, person) %>% filter(n()>1) %>% nrow(), 0)
``` 


# Save
```{r}
save(diary_social, diary, sex_long, network_nominations, network, s1_demo, s1_filter, s2_initial, s3_daily, s4_followup, s4_timespent, withfollowup, all_surveys, file = "data/cleaned_selected.rdata")
``` 


