---
pagetitle: "Goettingen Ovulatory Cycle Diaries 2"
---

# Goettingen Ovulatory Cycle Diaries 2 (GOCD2)

```{r message=FALSE, warning=FALSE}
source("0_helpers.R")
```


- [Data import](0_import_data.html): Here, we import the data and metadata from https://formr.org, the data collection study framework
- [Wrangle data](0_wrangle_data.html): Here, we wrangle the data into shape, estimate the fertile window, merge data from different sources, add human codings for freetext questions, etc.
- [Codebook](2_codebook.html): The codebook contains metadata, means, missingness, and further information on all variables collected in the study.
- [English codebook](2_codebook.html): Translated codebook. These translations are only there to help non-Germans read the codebook. They are not translated/backtranslated, nor heavily vetted. Be sure to use proper translation/back-translation if your goal is to reuse some of our items in an English setting.
- [Exclusion criteria](1_exclusion.html): We defined several criteria for women to be excluded in our analyses of ovulatory changes, these are computed here.
- [Descriptives](1_descriptives.html): Here, we summarise some of the descriptive information on this study on a higher-level than in the codebook.
- [Data anonymisation](3_anonymise_data.html): Our procedure to generate anonymised datasets.

We used these [helper functions](0_helpers.html). These are the [.Rprofile settings](.Rprofile.html).

See here for the documentation of [GOCD1](https://rubenarslan.github.io/ovulatory_shifts)

## Authors & Acknowledgements

### Authors
Julie Driebe & Ruben Arslan

### Acknowledgements


## Session info
```{r}
# Turn the .R files into .Rmd files, turn those into .html, remove the .Rmd files
# spin_R_files_to_site_html()
sessionInfo()
```
